Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-10-29 DryDep_supplement.tex
Finished first draft of section 2.

%\begin{minipage}[t]{1.\textwidth}
\subsection*{S.2 Tabulated parameters for stomatal conductance}
\appendixtables
\begin{sidewaystable}[!htbp]
  %\caption{S.2 Tabulated parameters for stomatal conductance}
  \begin{tabular}{lcccccccccccccc}
    \tophline
    Code & $g_\text{max}$ & $f_\text{min}$ & $\phi_a$ & $\phi_b$ & $\phi_c$ & $\phi_d$ & $\phi_e$ & $\phi_f$ & $\phi_\text{AS}$ & $\phi_\text{AE}$ & $f_\text{light}$ & $T_\text{min}$ & $T_\text{opt}$ & $T_\text{max}$ \\
    & (\unit{mmol\,s^{-1}\,\,m^{-2}}) &&&&&&&&&&&&&\\
    \middlehline
    CF & 140 & 0.1 & 0.8 & 0.8 & 0.8 & 0.8 & 1 & 1 & 0 & 0 & 0.006 & 0 & 18 & 36  \\
    DF & 150 & 0.1 & 0 & 0 & 1 & 0 & 20 & 30 & 0 & 0 & 0.006 & 0 & 20 & 35  \\
    NF & 200 & 0.1 & 1 & 1 & 0.2 & 1 & 130 & 60 & 80 & 35 & 0.013 & 8 & 25 & 38 \\
    BF & 200 & 0.02 & 1 & 1 & 0.3 & 1 & 130 & 60 & 80 & 35 & 0.009 & 1 & 23 & 39 \\
    TC & 300 & 0.1 & 0.1 & 1 & 0.1 & 0 & 45 & 0 & 0 & 0.0105 & 0.01 & 12 & 26 & 40 \\
    MC & 300 & 0.019 & 0.1 & 0.1 & 1 & 0.1 & 0 & 45 & 0 & 0 & 0.0048 & 0 & 25 & 51  \\
    RC & 360 & 0.02 & 0.2 & 0.2 & 1 & 0.2 & 20 & 45 & 0 & 0 & 0.0023 & 8 & 24 & 50  \\
    SNL & 60 & 0.01 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 0 & 0.009 & 1 & 18 & 36 \\
    GR & 270 & 0.01 & 1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 0.009 & 12 & 26 & 40 \\
    MS & 200 & 0.01 & 1 & 1 & 0.2 & 1 & 130 & 60 & 80 & 35 & 0.012 & 4 & 20 & 37 \\
    WE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    TU & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0  \\
    DE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0  \\
    W & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    ICE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    U & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    \bottomhline
  \end{tabular}
  \\
  \vspace{2\baselineskip}
  \begin{tabular}{lcccccccccccccc}
    \tophline
    Code & $D_\text{max}$ & $D_\text{min}$ & $D_\text{crit}$ & $R_\chem{SO}$ & $R_\chem{O_3}$ & height & $d_\text{SGS}$ & $d_\text{EGS}$ & $\nabla d_\text{SGS}$ & $\nabla d_\text{EGS}$ & $\text{LAI}_\text{min}$ & $\text{LAI}_\text{max}$ & LS & LE \\
    &&&&&&&&&&&&&& \\
    \middlehline
    CF & 0.5 & 3 & 1000 & 0 & 200 & 20 & 0 & 366 & 0 & 0 & 5 & 5 & 1 & 1\\
    DF & 1 & 3.25 & 1000 & 0 & 200 & 20 & 100 & 307 & 1.5 & -2.0 & 0 & 4 & 20 & 30\\
    NF & 1 & 3.2 & 1000 & 0 & 200 & 8 & 0 & 366 & 0 & 0 & 4 & 4 & 1 & 1\\
    BF & 2.2 & 4 & 1000 & 0 & 200 & 15 & 0 & 366 & 0 & 0 & 4 & 4 & 1 & 1\\
    TC & 1.2 & 3.2 & 8 & 0 & 200 & 1 & 123 & 213 & 2.57 & 2.57 & 0 & 3.5 & 70 & 20\\
    MC & 1 & 2.5 & 1000 & 0 & 200 & 2 & 123 & 237 & 2.57 & 2.57 & 0 & 3 & 70 & 44\\
    RC & 0.31 & 2.7 & 10 & 0 & 200 & 1 & 130 & 250 & 0 & 0 & 0 & 4.2 & 35 & 65\\
    SNL & 1.3 & 3 & 1000 & 0 & 400 & 0.5 & 0 & 366 & 0 & 0 & 2 & 3 & 192 & 96\\
    GR & 1.3 & 3 & 1000 & 0 & 1000 & 0.3 & 0 & 366 & 0 & 0 & 2 & 3.5 & 140 & 135\\
    MS & 1.3 & 3.2 & 1000 & 0 & 200 & 2 & 0 & 366 & 0 & 0 & 2.5 & 2.5 & 1 & 1\\
    WE  & 1 & 0 & 1000 & 50 & 400 & 0.5 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    TU & 1 & 0 & 1000 & 500 & 400 & 0.5 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    DE & 1 & 0 & 1000 & 1000 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    W  & 1 & 0 & 1000 & 1 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    ICE & 1 & 0 & 1000 & 1000 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    U & 1 & 0 & 1000 & 400 & 400 & 10 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    \bottomhline
  \end{tabular}
\end{sidewaystable}
%\end{minipage}

>>>>

%\begin{minipage}[t]{1.\textwidth}
\subsection*{S.2 Tabulated parameters for stomatal conductance}
\appendixtables
\begin{sidewaystable*}[!htbp]
  %\caption{S.2 Tabulated parameters for stomatal conductance}
  \begin{tabular}{lcccccccccccccc}
    \tophline
    Code$^*$ & $g_\text{max}$ & $f_\text{min}$ & $\phi_a$ & $\phi_b$ & $\phi_c$ & $\phi_d$ & $\phi_e$ & $\phi_f$ & $\phi_\text{AS}$ & $\phi_\text{AE}$ & $\alpha_\text{light}$ & $T_\text{min}$ & $T_\text{opt}$ & $T_\text{max}$ \\
    & (\unit{mmol\,s^{-1}\,m^{-2}}) &&&&&&(\unit{days})&(\unit{days})&(\unit{days})&(\unit{days})&&(\unit{^\circ C})&(\unit{^\circ C})&(\unit{^\circ C})\\
    \middlehline
    CF & 140 & 0.1 & 0.8 & 0.8 & 0.8 & 0.8 & 1 & 1 & 0 & 0 & 0.006 & 0 & 18 & 36  \\
    DF & 150 & 0.1 & 0 & 0 & 1 & 0 & 20 & 30 & 0 & 0 & 0.006 & 0 & 20 & 35  \\
    NF & 200 & 0.1 & 1 & 1 & 0.2 & 1 & 130 & 60 & 80 & 35 & 0.013 & 8 & 25 & 38 \\
    BF & 200 & 0.02 & 1 & 1 & 0.3 & 1 & 130 & 60 & 80 & 35 & 0.009 & 1 & 23 & 39 \\
    TC & 300 & 0.1 & 0.1 & 1 & 0.1 & 0 & 45 & 0 & 0 & 0.0105 & 0.01 & 12 & 26 & 40 \\
    MC & 300 & 0.019 & 0.1 & 0.1 & 1 & 0.1 & 0 & 45 & 0 & 0 & 0.0048 & 0 & 25 & 51  \\
    RC & 360 & 0.02 & 0.2 & 0.2 & 1 & 0.2 & 20 & 45 & 0 & 0 & 0.0023 & 8 & 24 & 50  \\
    SNL & 60 & 0.01 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 0 & 0.009 & 1 & 18 & 36 \\
    GR & 270 & 0.01 & 1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 0.009 & 12 & 26 & 40 \\
    MS & 200 & 0.01 & 1 & 1 & 0.2 & 1 & 130 & 60 & 80 & 35 & 0.012 & 4 & 20 & 37 \\
    WE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    TU & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0  \\
    DE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0  \\
    W & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    ICE & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    U & 0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 1 & 0 \\
    \bottomhline
  \end{tabular}
  \\
  \vspace{2\baselineskip}
  \begin{tabular}{lcccccccccccccc}
    \tophline
    Code$^*$ & $D_\text{max}$ & $D_\text{min}$ & $D_\text{crit}$ & $R_\chem{SO}$ & $R_\chem{O_3}$ & $h$ & $d_\text{SGS}$ & $d_\text{EGS}$ & $\nabla d_\text{SGS}$ & $\nabla d_\text{EGS}$ & $\text{LAI}_\text{min}$ & $\text{LAI}_\text{max}$ & LS & LE \\
    &(\unit{kPA})&(\unit{kPa})&(\unit{kPa})&(\unit{s\,m^{-1}})&(\unit{s\,m^{-1}})&(\unit{m})&(\unit{day})&(\unit{day})&(\unit{days/^\circ lat})&(\unit{days/^\circ lat})&(\unit{m^2\,m^{-2}})&(\unit{m^2\,m^{-2}})&(\unit{days})&(\unit{days}) \\
    \middlehline
    CF & 0.5 & 3 & 1000 & 0 & 200 & 20 & 0 & 366 & 0 & 0 & 5 & 5 & 1 & 1\\
    DF & 1 & 3.25 & 1000 & 0 & 200 & 20 & 100 & 307 & 1.5 & -2.0 & 0 & 4 & 20 & 30\\
    NF & 1 & 3.2 & 1000 & 0 & 200 & 8 & 0 & 366 & 0 & 0 & 4 & 4 & 1 & 1\\
    BF & 2.2 & 4 & 1000 & 0 & 200 & 15 & 0 & 366 & 0 & 0 & 4 & 4 & 1 & 1\\
    TC & 1.2 & 3.2 & 8 & 0 & 200 & 1 & 123 & 213 & 2.57 & 2.57 & 0 & 3.5 & 70 & 20\\
    MC & 1 & 2.5 & 1000 & 0 & 200 & 2 & 123 & 237 & 2.57 & 2.57 & 0 & 3 & 70 & 44\\
    RC & 0.31 & 2.7 & 10 & 0 & 200 & 1 & 130 & 250 & 0 & 0 & 0 & 4.2 & 35 & 65\\
    SNL & 1.3 & 3 & 1000 & 0 & 400 & 0.5 & 0 & 366 & 0 & 0 & 2 & 3 & 192 & 96\\
    GR & 1.3 & 3 & 1000 & 0 & 1000 & 0.3 & 0 & 366 & 0 & 0 & 2 & 3.5 & 140 & 135\\
    MS & 1.3 & 3.2 & 1000 & 0 & 200 & 2 & 0 & 366 & 0 & 0 & 2.5 & 2.5 & 1 & 1\\
    WE  & 1 & 0 & 1000 & 50 & 400 & 0.5 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    TU & 1 & 0 & 1000 & 500 & 400 & 0.5 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    DE & 1 & 0 & 1000 & 1000 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    W  & 1 & 0 & 1000 & 1 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    ICE & 1 & 0 & 1000 & 1000 & 2000 & 0 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    U & 1 & 0 & 1000 & 400 & 400 & 10 & 0 & 366 & 0 & 0 & 0 & 0 & 0 & 0\\
    \bottomhline
  \end{tabular}
  \belowtable{$^*$: CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean scrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}
\end{sidewaystable*}
%\end{minipage}
